QPLIB: A Library of Quadratic Programming Instances

### 2016-07-28 QPLIB.tex
nimg: added QPLIB format section, currently in appendix       Updated main document to reflect this, and added nimg coordinates       Alightly updated Section 3 to reflect QPLIB format
Pietro's affiliation
included Nick's comments

@@

\institute{Fabio Furini \at
           LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France,
           \email{fabio.furini@dauphine.fr}
%
\and       
           Emiliano Traversi \at
           LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France.
           \email{emiliano.traversi@lipn.fr}
%
\and       Alper Atamturk \at
%
\and       Pietro Belotti \at
%
\and       Pierre Bonami \at 
%
\and       Sourour Elloumi \at
%
\and       Antonio Frangioni \at
           Dipartimento di Informatica, Universit\`a di Pisa,
           Largo B. Pontecorvo 2, 56127 Pisa, Italy,
           \email{frangio@di.unipi.it}
%
\and       Ambros Gleixner \at
           Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany. 
           \email{gleixner@zib.de}
%
\and       Nick Gould \at 
%
\and       Leo Liberti \at
           CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France.
           \email{liberti@lix.polytechnique.fr}
%
\and       Andrea Lodi \at
           Ecole Polytechnique de Montréal, Canada.               \email{andrea.lodi@polymtl.ca}
%
\and       Ruth Misener \at
%
\and       Hans Mittelmann \at
           School of Mathematical and Statistical Sciences, Arizona State University,      Tempe, AZ 85287-1804, U.S.A.
\email{mittelmann@asu.edu}
%
\and       Nick Sahinidis \at 
%
\and       Frederic Roupin \at 
%
\and       Stefan Vigerske \at 
           GAMS Software GmbH, P.O. Box 40 59,50216 Frechen, Germany
           \email{stefan@gams.com}
%
\and       Angelika Wiegele \at
           }

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP). QP is a very ``varied'' class, comprising sub-classes of problems ranging from trivial to undecidable. Solution methods for QP are very diverse, ranging from entirely combinatorial ones to completely continuous ones, including many for which both aspects are fundamental. Selecting a set of instances of QP that is at the same time not overwhelmingly difficult and sufficiently challenging for the many different interested communities is therefore important. 
 %In order to help our selection process 
 We propose a simple taxonomy for QP instances that leads to a systematic problem selection mechanism. We then briefly survey the field of QP, giving an overview of theory, methods and solvers. Finally we describe how the library was put together, and detail its final contents.
\end{abstract}

@@

>>>>

\usepackage{longtable}
\usepackage{enumitem}
\usepackage{calc}

@@

\institute{Fabio Furini \at
           LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France,
           \email{fabio.furini@dauphine.fr}
%
\and
           Emiliano Traversi \at
           LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France.
           \email{emiliano.traversi@lipn.fr}
%
\and       Alper Atamturk \at
%
\and       Pietro Belotti \at
           Xpress-Optimizer team, FICO, Birmingham UK
           \email{pietrobelotti@fico.com}
%
\and       Pierre Bonami \at
%
\and       Sourour Elloumi \at
%
\and       Antonio Frangioni \at
           Dipartimento di Informatica, Universit\`a di Pisa,
           Largo B. Pontecorvo 2, 56127 Pisa, Italy,
           \email{frangio@di.unipi.it}
%
\and       Ambros Gleixner \at
           Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{gleixner@zib.de}
%
\and       Nick Gould \at
           STFC-Rutherford Appleton Laboratory, Chilton, Oxfordshire OX11 0QX,
           England.
           \email{nick.gould@stfc.ac.uk}
%
\and       Leo Liberti \at
           CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France.
           \email{liberti@lix.polytechnique.fr}
%
\and       Andrea Lodi \at
           Ecole Polytechnique de Montréal, Canada.               \email{andrea.lodi@polymtl.ca}
%
\and       Ruth Misener \at
%
\and       Hans Mittelmann \at
           School of Mathematical and Statistical Sciences, Arizona State University,      Tempe, AZ 85287-1804, U.S.A.
\email{mittelmann@asu.edu}
%
\and       Nick Sahinidis \at
%
\and       Frederic Roupin \at
%
\and       Stefan Vigerske \at
           GAMS Software GmbH, P.O. Box 40 59,50216 Frechen, Germany
           \email{stefan@gams.com}
%
\and       Angelika Wiegele \at
           }

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP).
 QP is a very ``varied'' class, comprising sub-classes of problems ranging from
 trivial to undecidable. Solution methods for QP are very diverse, ranging from
 entirely combinatorial ones to completely continuous ones, including many for
 which both aspects are fundamental. Selecting a set of instances of QP that is
 at the same time not overwhelmingly numerous and sufficiently challenging for the
 many different interested communities is therefore important. We propose a simple
 taxonomy for QP instances that leads to a systematic problem selection mechanism.
 We then briefly survey the field of QP, giving an overview of theory, methods and
 solvers. Finally we describe how the library was put together, and detail its final
 contents.
\end{abstract}

@@

%  QPLIB format. Move to main text?

\input{format.tex}
